Hydras and Cie \\ Variations on Kirby \& Paris' hydra battles and ordinal numbers in Coq

### 2021-09-24 doc/JFLA2022/paper.tex
fix a few typos
Add citations.

\subsection{Vision}
The \emph{Hydra-battles} project, part of \emph{Coq-Community}~\cite{CoqCommunity} aims to be an experimental platform for the collaborative development of commented libraries of formal proofs. \emph{Coq-Community} is a community organization that we have founded in 2018 with two goals in mind: providing a solution for the long-term maintenance of interesting Coq packages, and working collaboratively on documentation projects. The \emph{Hydra-battles} project demonstrates that these two goals are not independent: interesting Coq packages can become the basis for new documentation.
%
This umbrella project now includes evolved versions of former \emph{contribs} Cantor and Additions (under the new names of Hydra-battles and Addition-chains), the Pocklington library, extracted from Russel O'Connor's Goedel \emph{contrib} and a bridge to the Gaia library (\emph{contrib} of José Grimm).
%
By following this approach of commenting interesting Coq packages, we provide new documentation content, that contributes to the diversity of the thriving Coq documentation ecosystem.

@@

Futhermore, contrary to traditionally published books, the ``book'' that forms part of this project is intended to be forever evolving. As new Coq formalization patterns and proof techniques appear, the book can be adapted to demonstrate their use (in case they fit well with our applications).
%
By using modern maintenance techniques such as continuous integration and deployment, we can ensure that this documentation stays up to date with the latest Coq releases. With Alectryon, we ensure that code and documentation are always in sync.

>>>>

\subsection{Vision}
The \emph{Hydra-battles} project, part of \emph{Coq-Community}~\cite{CoqCommunity} aims to be an experimental platform for the collaborative development of commented libraries of formal proofs. \emph{Coq-Community} is a community organization that we have founded in 2018 with two goals in mind: providing a solution for the long-term maintenance of interesting Coq packages, and working collaboratively on documentation projects. The \emph{Hydra-battles} project demonstrates that these two goals are not independent: interesting Coq packages can become the basis for new documentation.
%
This umbrella project now includes evolved versions of former \emph{contribs} Cantor and Additions (under the new names of Hydra-battles and Addition-chains), the Pocklington library, extracted from Russel O'Connor's Goedel \emph{contrib}\cite{OConnor05, Goedel} and a bridge to the Gaia library (\emph{contrib} of José Grimm~\cite{Gaia,grimm:hal-00911710}).
%
By following this approach of commenting interesting Coq packages, we provide new documentation content, that contributes to the diversity of the thriving Coq documentation ecosystem.

@@

Futhermore, contrary to traditionally published books, the ``book'' that forms part of this project is intended to be forever evolving. As new Coq formalization patterns and proof techniques appear, the book can be adapted to demonstrate their use (in case they fit well with our applications).
%
By using modern maintenance techniques such as continuous integration and deployment, we can ensure that this documentation stays up to date with the latest Coq releases. With Alectryon~\cite{alectryonpaper, alectryongithub}, we ensure that code and documentation are always in sync.
